Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 ch1/chapter-introduction.tex
add a changelog, begin introduction text, comment out old protochapters

TBD

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{ch1/figs/test1}
  \end{center}
  \caption[Test fig]{This is a placeholder.}
\end{figure}

>>>>

Technology and ideas catalyze discovery.  Astronomical technology development started 405 years ago with Galileo's 2 inch telescope and \emph{Sidereus Nucius}.  Today there are sixteen optical telescopes with diameters of 6.5 meters or larger, and there are IPython Jupyter Notebooks\footnote{\url{https://jupyter.org/}}\footnote{Galileo's detailed notebooks of Jupiter contained observational data, calculations, figures, and explanatory material, and were, in part, the inspiration for the name of Jupyter Notebooks.  The \emph{py} is for python, naturally.}  This PhD dissertation  pushes the frontier of both scientific technology and observational astronomy.  There are two main threads.  First, I developed silicon diffractive optics for high resolution near infarared astronomical spectroscopy.  The devices leverage high precision silicon semiconductor lithography to provide optical quality diffraction grooves.

### 2015-03-25 gullydiss.tex
add a changelog, begin introduction text, comment out old protochapters

This multipurpose document serves, among other purposes, as a process manual, design guide, journal of recent progress, enhanced lab notebook, and iSHELL delivery document.  The ultimate goal is to include detailed explanative material as appendix chapters in my dissertation, which for now appear as full-fledged chapters.  The reason for including detailed explanative material is that a small subset of future workers trying to replicate my results may want to know the detailed process strategy, and how we arrived at our strategy.  An innumerable number of variables affect the production of our diffraction gratings.  We simply do not have enough time to experiment with and characterize every variable.  For example, what is the effect of the post-spin bake time on thick Si substrates?  The cost of and risk of damage to the thick substrates needed to answer that question is prohibitively high, so experimenting with this process step has not been attempted.  Instead we use our best guess for what is a good baking time and stick with it.  In this document I attempt to explain our reasoning for choices like these.  Other process variables can be characterized and controlled- I chronicle this journey here in detail.  Sometimes we go down the wrong path and our ostensible solutions degrade performance and foil our progress, for days or months.  It is informative to describe the journey for the benefit of future researchers in this area.  These sorts of descriptions usually garner only one sentence or paragraph in a much longer published journal.  Rightfully so- it would be daunting to separate the wheat from the chaff if each folly were offered the same airtime as the more rare success.  But here is my chance to record those follies and tell the story to those internal members who may be interested.  Lastly, I have attempted to include informative diagrams and cartoons, and at times the density of documents may be overkill.  I am still working out the optimal tradeoff in text and figures and tables.  Comments are welcome.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Actual text starts here.					     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Including external files for each chapter makes this document simpler,
% makes each chapter simpler, and allows for generating test documents
% with as few as zero chapters (by commenting out the include statements).
% This allows quicker processing by the Makediss command file in case you
% are not working on a specific, long and slow to compile chapter. You
% can even change the chapter order by merely interchanging the order
% of the include statements (something I found helpful in my own
% dissertation).
%
\include{ch1/chapter-introduction}
\include{chGratingDesign/chapter-gratingdesign}
\include{chGratingProcess/chapter-gratingprocess}
\include{chIshell/chapter-ishellgratings}
\include{chFabryPerot/chapter-fabryperot}

@@

\include{appendices/chapter-appendix2}

\include{appendices/chapter-appendix01-S1800}

>>>>

This is where the abstract goes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Actual text starts here.					     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Including external files for each chapter makes this document simpler,
% makes each chapter simpler, and allows for generating test documents
% with as few as zero chapters (by commenting out the include statements).
% This allows quicker processing by the Makediss command file in case you
% are not working on a specific, long and slow to compile chapter. You
% can even change the chapter order by merely interchanging the order
% of the include statements (something I found helpful in my own
% dissertation).
%
\include{ch1/chapter-introduction}
%\include{chGratingDesign/chapter-gratingdesign}
%\include{chGratingProcess/chapter-gratingprocess}
%\include{chIshell/chapter-ishellgratings}
%\include{chFabryPerot/chapter-fabryperot}

@@

%\include{appendices/chapter-appendix2}

%\include{appendices/chapter-appendix01-S1800}
